\documentclass[letterpaper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[arabic,english]{babel} % Add arabic for potential future use or context, default to english for resume content
\usepackage{geometry}
\geometry{left=0.75in, right=0.75in, top=0.75in, bottom=0.75in}
\usepackage{enumitem}
\setlist[itemize]{itemsep=0pt, parsep=0pt, topsep=2pt, partopsep=0pt, leftmargin=1em}
\usepackage{titlesec}
	itlespacing*{\section}{0pt}{8pt}{4pt} % Adjust spacing for sections
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
    citecolor=black,
    filecolor=black,
    menucolor=black,
    anchorcolor=black
}
\usepackage{ragged2e} % For \Justifying
\usepackage{xurl} % For better URL line breaks

\pagestyle{empty} % No page numbers

% Define a new command for section titles

ewcommand{\resSection}[1]{\section*{\MakeUppercase{#1}}\vspace{-0.1cm}\hrule\vspace{0.1cm}}

\begin{document}
\Justifying % Justify text for a clean look

% --- Header ---
\begin{center}
    	extbf{\Large John Doe} \\
    \href{mailto:john.doe@example.com}{\color{black}john.doe@example.com} 	extbullet \ (123) 456-7890 	extbullet \ \href{https://www.linkedin.com/in/johndoe}{\color{blue}linkedin.com/in/johndoe} 	extbullet \ San Francisco, CA
\end{center}
\vspace{-0.2cm} % Adjust space after header

% --- Professional Summary ---
\resSection{Professional Summary}
A highly motivated and results-oriented professional with 	extbf{7+ years of experience} in software development, specializing in building scalable and robust applications. Proven ability to lead complex projects, optimize system performance, and mentor junior engineers. Seeking a challenging Senior Software Engineer role to leverage expertise in full-stack development and contribute to innovative product solutions.

% --- Work Experience ---
\resSection{Work Experience}

	extbf{Senior Software Engineer} \hfill 	extbf{Jan 2020 – Present} \\
	extit{Tech Solutions Inc.} \hfill 	extit{San Francisco, CA}
\begin{itemize}
    \item Developed and maintained high-performance backend services using Python and Django, handling millions of requests daily.
    \item Collaborated with product management and design teams to translate business requirements into technical specifications and deliver new features.
    \item Optimized critical database queries and API endpoints, resulting in a 	extbf{20\% reduction} in average response times.
    \item Led code reviews, ensuring code quality, maintainability, and adherence to best practices for a team of 5 developers.
    \item Mentored junior engineers, fostering their professional growth and improving team productivity.
\end{itemize}

\vspace{0.1cm}

	extbf{Software Developer} \hfill 	extbf{Jun 2017 – Dec 2019} \\
	extit{Innovate Corp.} \hfill 	extit{New York, NY}
\begin{itemize}
    \item Built responsive and intuitive user interfaces using React.js and Redux, enhancing user experience for enterprise applications.
    \item Participated actively in Agile/Scrum development cycles, contributing to daily stand-ups, sprint planning, and retrospectives.
    \item Developed and consumed RESTful APIs to integrate frontend components with backend services.
    \item Wrote comprehensive unit and integration tests using Jest and Enzyme, increasing code coverage by 30\%.
\end{itemize}

% --- Education ---
\resSection{Education}

	extbf{Master of Science in Computer Science} \hfill 	extbf{May 2017} \\
	extit{University of California, Berkeley} \hfill 	extit{Berkeley, CA}
\vspace{0.1cm}

	extbf{Bachelor of Science in Computer Engineering} \hfill 	extbf{May 2015} \\
	extit{State University} \hfill 	extit{Anytown, USA}

% --- Skills ---
\resSection{Skills}
	extbf{Programming Languages:} Python, Java, JavaScript, C++, Go, Ruby \\
	extbf{Web Technologies:} React.js, Node.js, Django, Flask, RESTful APIs, HTML5, CSS3 \\
	extbf{Databases:} PostgreSQL, MySQL, MongoDB, Redis \\
	extbf{Tools \& Platforms:} Docker, Kubernetes, AWS (EC2, S3, RDS), Git, Jira, Jenkins \\
	extbf{Methodologies:} Agile, Scrum, Test-Driven Development (TDD), CI/CD

\end{document}